---
title: "forFactsheet"
output: html_document
date: "2025-07-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(mlr3learners) 
require(kknn)  
require(class)
require(ggplot2)
library(mlr3)
library(mlr3viz)
library(ggplot2)
library(data.table)
library(sqldf)
library(ggplot2)
library(labelled)
library(sqldf)
library(tidyr)  # for pivot_wider
library(dplyr)
library(janitor)
```


##Demographics
```{r}
demo <- fread("~/Desktop/GRIT/Kibera/subsetCsv/demographics.csv", header = TRUE)
labelled_data <- readRDS("~/Desktop/GRIT/Kibera/codebook/codebook_labelled_data.rds")
```
```{r}
# make var numeric
numericVars <- c("x1.1", "x1.2", "x1.3", "x2.1", "x3.1_1_TEXT", "x3.9" )
for (col in numericVars) {
  demo[[col]] <- as.numeric(as.character(demo[[col]]))
}

# make var date
demo$x1.4 <- as.Date(demo$x1.4, format = "%d/%m/%Y")

# make var string
charVars <- c("x2.5_5_TEXT" , "x2.7_6_TEXT", "x2.10_8_TEXT", "x2.12_10_TEXT", "x2.14_5_TEXT", "x2.16_7_TEXT", "x2.21_9_TEXT", "x3.3_7_TEXT", "x3.13_8_TEXT", 
              "x3.14_7_TEXT", "x3.17_7_TEXT", "x4.10_1_TEXT", "x7.9_6_TEXT") 

for (col in charVars) {
  demo[[col]] <- as.character(demo[[col]])
}


#for (col in factorVars) {
  #data[[col]] <- as.factor(data[[col]])
#}


allVars <- names(demo)
excludeVars <- c(numericVars, charVars, "x1.4")
factorVars <- setdiff(allVars, excludeVars)


for (col in factorVars) {
  demo[[col]] <- as.character(demo[[col]])
}
```

```{r}
# Get overlapping variables
common_vars <- intersect(names(demo), names(labelled_data))

print(common_vars)

# Identify non-numeric variables
non_numeric_vars <- common_vars[
  sapply(common_vars, function(var) {
    !is.numeric(demo[[var]]) && !is.numeric(labelled_data[[var]])
  })
]

# Apply labels to non-numeric overlapping variables only
for (var in non_numeric_vars) {
  var_label(demo[[var]]) <- var_label(labelled_data[[var]])
  val_labels(demo[[var]]) <- val_labels(labelled_data[[var]])
}

unique(demo[["x2.2"]])

```

```{r}

demo$x2.2_factor <- to_factor(demo$x2.2, levels = "label")
demo$x2.7_factor <- to_factor(demo$x2.7, levels = "label")
demo$x2.8_factor  <- to_factor(demo$x2.8, levels = "label")
demo$x2.9_factor <- to_factor(demo$x2.9, levels = "label")
demo$x2.16_factor <- to_factor(demo$x2.16, levels = "label")

demo$x2.17_factor  <- to_factor(demo$x2.17, levels = "label")


sql_result <- sqldf("
  SELECT
    [x2.7_factor],
    COUNT(*) AS count
  FROM demo
  GROUP BY [x2.7_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, dv as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x2.7_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```


## Mental Health
```{r}

mentalHealth <- fread("~/Desktop/GRIT/Kibera/subsetCsv/mentalHealth.csv", header = TRUE)
labelled_data <- readRDS("~/Desktop/GRIT/Kibera/codebook/codebook_labelled_data.rds")
```

```{r}
# make var numeric
numericVars <- c("x1.1", "x1.2", "x1.3", "x2.1", "x3.1_1_TEXT", "x3.9" )
for (col in numericVars) {
  mentalHealth[[col]] <- as.numeric(as.character(mentalHealth[[col]]))
}

# make var date
mentalHealth$x1.4 <- as.Date(mentalHealth$x1.4, format = "%d/%m/%Y")

# make var string
charVars <- c("x2.5_5_TEXT" , "x2.7_6_TEXT", "x2.10_8_TEXT", "x2.12_10_TEXT", "x2.14_5_TEXT", "x2.16_7_TEXT", "x2.21_9_TEXT", "x3.3_7_TEXT", "x3.13_8_TEXT", 
              "x3.14_7_TEXT", "x3.17_7_TEXT", "x4.10_1_TEXT", "x7.9_6_TEXT") 

for (col in charVars) {
  mentalHealth[[col]] <- as.character(mentalHealth[[col]])
}


#for (col in factorVars) {
  #data[[col]] <- as.factor(data[[col]])
#}


allVars <- names(mentalHealth)
excludeVars <- c(numericVars, charVars, "x1.4")
factorVars <- setdiff(allVars, excludeVars)


for (col in factorVars) {
  mentalHealth[[col]] <- as.character(mentalHealth[[col]])
}
```

```{r}
# Get overlapping variables
common_vars <- intersect(names(mentalHealth), names(labelled_data))

print(common_vars)

# Identify non-numeric variables
non_numeric_vars <- common_vars[
  sapply(common_vars, function(var) {
    !is.numeric(mentalHealth[[var]]) && !is.numeric(labelled_data[[var]])
  })
]

# Apply labels to non-numeric overlapping variables only
for (var in non_numeric_vars) {
  var_label(mentalHealth[[var]]) <- var_label(labelled_data[[var]])
  val_labels(mentalHealth[[var]]) <- val_labels(labelled_data[[var]])
}

unique(mentalHealth[["x2.2"]])

```

```{r}
mentalHealth$x2.2_factor <- to_factor(mentalHealth$x2.2, levels = "label")

sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [PHQ9Level],
    COUNT(*) AS count
  FROM mentalHealth
  GROUP BY [x2.2_factor], [PHQ9Level]
  ORDER BY [x2.2_factor], [PHQ9Level]
")

# Step 2: Pivot to make a wide table (Age as rows, dv as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = PHQ9Level,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```


```{r}
mentalHealth$x2.2_factor <- to_factor(mentalHealth$x2.2, levels = "label")
demo$x1.1_factor <- to_factor(demo$x1.1, levels = "label")

sql_result <- sqldf("
  SELECT
    d.[x1.1],
    m.[PHQ9Level],
    COUNT(*) AS count
  FROM mentalHealth AS m
  JOIN demo AS d
    ON m.[x1.2] = d.[x1.2]
  GROUP BY d.[x1.1], m.[PHQ9Level]
  ORDER BY d.[x1.1], m.[PHQ9Level]
")

# Step 2: Pivot to make a wide table (Age as rows, dv as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = PHQ9Level,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)


```


## Gender Perceptions
```{r}
gender <- fread("~/Desktop/GRIT/Kibera/subsetCsv/genderPerceptions.csv", header = TRUE)
labelled_data <- readRDS("~/Desktop/GRIT/Kibera/codebook/codebook_labelled_data.rds")
```

```{r}
# make var numeric
numericVars <- c("x1.1", "x1.2", "x1.3", "x2.1", "x3.1_1_TEXT", "x3.9" )
for (col in numericVars) {
  gender[[col]] <- as.numeric(as.character(gender[[col]]))
}

# make var date
gender$x1.4 <- as.Date(gender$x1.4, format = "%d/%m/%Y")

# make var string
charVars <- c("x2.5_5_TEXT" , "x2.7_6_TEXT", "x2.10_8_TEXT", "x2.12_10_TEXT", "x2.14_5_TEXT", "x2.16_7_TEXT", "x2.21_9_TEXT", "x3.3_7_TEXT", "x3.13_8_TEXT", 
              "x3.14_7_TEXT", "x3.17_7_TEXT", "x4.10_1_TEXT", "x7.9_6_TEXT") 

for (col in charVars) {
  gender[[col]] <- as.character(gender[[col]])
}


#for (col in factorVars) {
  #data[[col]] <- as.factor(data[[col]])
#}


allVars <- names(gender)
excludeVars <- c(numericVars, charVars, "x1.4")
factorVars <- setdiff(allVars, excludeVars)


for (col in factorVars) {
  gender[[col]] <- as.character(gender[[col]])
}
```

```{r}
# Get overlapping variables
common_vars <- intersect(names(gender), names(labelled_data))

print(common_vars)

# Identify non-numeric variables
non_numeric_vars <- common_vars[
  sapply(common_vars, function(var) {
    !is.numeric(gender[[var]]) && !is.numeric(labelled_data[[var]])
  })
]

# Apply labels to non-numeric overlapping variables only
for (var in non_numeric_vars) {
  var_label(gender[[var]]) <- var_label(labelled_data[[var]])
  val_labels(gender[[var]]) <- val_labels(labelled_data[[var]])
}

unique(gender[["x2.2"]])

```


```{r}
gender$x8.1_factor <- to_factor(gender$x8.1, levels = "label")
gender$x8.2_factor <- to_factor(gender$x8.2, levels = "label")
gender$x8.3_factor <- to_factor(gender$x8.3, levels = "label")
gender$x8.4_factor <- to_factor(gender$x8.4, levels = "label")
gender$x8.5_factor <- to_factor(gender$x8.5, levels = "label")

gender$x8.6_factor <- to_factor(gender$x8.6, levels = "label")
gender$x8.7_factor <- to_factor(gender$x8.7, levels = "label")
gender$x8.8_factor <- to_factor(gender$x8.8, levels = "label")
gender$x8.9_factor <- to_factor(gender$x8.9, levels = "label")
gender$x2.2_factor <- to_factor(gender$x2.2, levels = "label")
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x8.1_factor],
    COUNT(*) AS count
  FROM gender
  GROUP BY [x2.2_factor], [x8.1_factor]
  ORDER BY [x2.2_factor], [x8.1_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x8.1_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x8.2_factor],
    COUNT(*) AS count
  FROM gender
  GROUP BY [x2.2_factor], [x8.2_factor]
  ORDER BY [x2.2_factor], [x8.2_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x8.2_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x8.3_factor],
    COUNT(*) AS count
  FROM gender
  GROUP BY [x2.2_factor], [x8.3_factor]
  ORDER BY [x2.2_factor], [x8.3_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x8.3_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x8.4_factor],
    COUNT(*) AS count
  FROM gender
  GROUP BY [x2.2_factor], [x8.4_factor]
  ORDER BY [x2.2_factor], [x8.4_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x8.4_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x8.5_factor],
    COUNT(*) AS count
  FROM gender
  GROUP BY [x2.2_factor], [x8.5_factor]
  ORDER BY [x2.2_factor], [x8.5_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x8.5_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```


```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x8.6_factor],
    COUNT(*) AS count
  FROM gender
  GROUP BY [x2.2_factor], [x8.6_factor]
  ORDER BY [x2.2_factor], [x8.6_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x8.6_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x8.7_factor],
    COUNT(*) AS count
  FROM gender
  GROUP BY [x2.2_factor], [x8.7_factor]
  ORDER BY [x2.2_factor], [x8.7_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x8.7_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x8.8_factor],
    COUNT(*) AS count
  FROM gender
  GROUP BY [x2.2_factor], [x8.8_factor]
  ORDER BY [x2.2_factor], [x8.8_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x8.8_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x8.9_factor],
    COUNT(*) AS count
  FROM gender
  GROUP BY [x2.2_factor], [x8.9_factor]
  ORDER BY [x2.2_factor], [x8.9_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x8.9_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

## Domestic Violence
```{r}
dv <- fread("~/Desktop/GRIT/Kibera/subsetCsv/domesticViolence.csv", header = TRUE)
labelled_data <- readRDS("~/Desktop/GRIT/Kibera/codebook/codebook_labelled_data.rds")
```

```{r}
# make var numeric
numericVars <- c("x1.1", "x1.2", "x1.3", "x2.1", "x3.1_1_TEXT", "x3.9" )
for (col in numericVars) {
  dv[[col]] <- as.numeric(as.character(dv[[col]]))
}

# make var date
dv$x1.4 <- as.Date(dv$x1.4, format = "%d/%m/%Y")

# make var string
charVars <- c("x2.5_5_TEXT" , "x2.7_6_TEXT", "x2.10_8_TEXT", "x2.12_10_TEXT", "x2.14_5_TEXT", "x2.16_7_TEXT", "x2.21_9_TEXT", "x3.3_7_TEXT", "x3.13_8_TEXT", 
              "x3.14_7_TEXT", "x3.17_7_TEXT", "x4.10_1_TEXT", "x7.9_6_TEXT") 

for (col in charVars) {
  dv[[col]] <- as.character(dv[[col]])
}


#for (col in factorVars) {
  #data[[col]] <- as.factor(data[[col]])
#}


allVars <- names(dv)
excludeVars <- c(numericVars, charVars, "x1.4")
factorVars <- setdiff(allVars, excludeVars)


for (col in factorVars) {
  dv[[col]] <- as.character(dv[[col]])
}
```

```{r}
# Get overlapping variables
common_vars <- intersect(names(dv), names(labelled_data))

print(common_vars)

# Identify non-numeric variables
non_numeric_vars <- common_vars[
  sapply(common_vars, function(var) {
    !is.numeric(dv[[var]]) && !is.numeric(labelled_data[[var]])
  })
]

# Apply labels to non-numeric overlapping variables only
for (var in non_numeric_vars) {
  var_label(dv[[var]]) <- var_label(labelled_data[[var]])
  val_labels(dv[[var]]) <- val_labels(labelled_data[[var]])
}

unique(dv[["x2.2"]])

```
```{r}
dv$x6.1_factor <- to_factor(dv$x6.1, levels = "label")
dv$x6.2_factor <- to_factor(dv$x6.2, levels = "label")
dv$x6.3_factor <- to_factor(dv$x6.3, levels = "label")
dv$x6.4_factor <- to_factor(dv$x6.4, levels = "label")
dv$x2.2_factor <- to_factor(dv$x2.2, levels = "label")
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x6.1_factor],
    COUNT(*) AS count
  FROM dv
  GROUP BY [x2.2_factor], [x6.1_factor]
  ORDER BY [x2.2_factor], [x6.1_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x6.1_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x6.1_factor],
    COUNT(*) AS count
  FROM dv
  GROUP BY [x2.1], [x6.1_factor]
  ORDER BY [x2.1], [x6.1_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x6.1_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```




```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x6.2_factor],
    COUNT(*) AS count
  FROM dv
  GROUP BY [x2.2_factor], [x6.2_factor]
  ORDER BY [x2.2_factor], [x6.2_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x6.2_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x6.3_factor],
    COUNT(*) AS count
  FROM dv
  GROUP BY [x2.2_factor], [x6.3_factor]
  ORDER BY [x2.2_factor], [x6.3_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x6.3_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```
```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x6.4_factor],
    COUNT(*) AS count
  FROM dv
  GROUP BY [x2.2_factor], [x6.4_factor]
  ORDER BY [x2.2_factor], [x6.4_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x6.4_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

## Abortion

```{r}
abortion <- fread("~/Desktop/GRIT/Kibera/subsetCsv/abortion.csv", header = TRUE)
labelled_data <- readRDS("~/Desktop/GRIT/Kibera/codebook/codebook_labelled_data.rds")
```

```{r}
# make var numeric
numericVars <- c("x1.1", "x1.2", "x1.3", "x2.1", "x3.1_1_TEXT", "x3.9" )
for (col in numericVars) {
  abortion[[col]] <- as.numeric(as.character(abortion[[col]]))
}

# make var date
abortion$x1.4 <- as.Date(abortion$x1.4, format = "%d/%m/%Y")

# make var string
charVars <- c("x2.5_5_TEXT" , "x2.7_6_TEXT", "x2.10_8_TEXT", "x2.12_10_TEXT", "x2.14_5_TEXT", "x2.16_7_TEXT", "x2.21_9_TEXT", "x3.3_7_TEXT", "x3.13_8_TEXT", 
              "x3.14_7_TEXT", "x3.17_7_TEXT", "x4.10_1_TEXT", "x7.9_6_TEXT") 

for (col in charVars) {
  abortion[[col]] <- as.character(abortion[[col]])
}


#for (col in factorVars) {
  #data[[col]] <- as.factor(data[[col]])
#}


allVars <- names(abortion)
excludeVars <- c(numericVars, charVars, "x1.4")
factorVars <- setdiff(allVars, excludeVars)


for (col in factorVars) {
  abortion[[col]] <- as.character(abortion[[col]])
}
```

```{r}
# Get overlapping variables
common_vars <- intersect(names(abortion), names(labelled_data))

print(common_vars)

# Identify non-numeric variables
non_numeric_vars <- common_vars[
  sapply(common_vars, function(var) {
    !is.numeric(abortion[[var]]) && !is.numeric(labelled_data[[var]])
  })
]

# Apply labels to non-numeric overlapping variables only
for (var in non_numeric_vars) {
  var_label(abortion[[var]]) <- var_label(labelled_data[[var]])
  val_labels(abortion[[var]]) <- val_labels(labelled_data[[var]])
}

unique(abortion[["x2.2"]])

```



```{r}
abortion$x3.15_factor <- to_factor(abortion$x3.15, levels = "label")
abortion$x3.16_factor <- to_factor(abortion$x3.16, levels = "label")
abortion$x3.17_factor <- to_factor(abortion$x3.17, levels = "label")

abortion$x2.2_factor <- to_factor(abortion$x2.2, levels = "label")
```


```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.15_factor],
    COUNT(*) AS count
  FROM abortion
  GROUP BY [x2.2_factor], [x3.15_factor]
  ORDER BY [x2.2_factor], [x3.15_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.15_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.16_factor],
    COUNT(*) AS count
  FROM abortion
  GROUP BY [x2.2_factor], [x3.16_factor]
  ORDER BY [x2.2_factor], [x3.16_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.16_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```
```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.17_factor],
    COUNT(*) AS count
  FROM abortion
  GROUP BY [x2.2_factor], [x3.17_factor]
  ORDER BY [x2.2_factor], [x3.17_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.17_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```


## Personal Sexual Health
```{r}
sexual <- fread("~/Desktop/GRIT/Kibera/subsetCsv/sex.csv", header = TRUE)
labelled_data <- readRDS("~/Desktop/GRIT/Kibera/codebook/codebook_labelled_data.rds")
```

```{r}
# make var numeric
numericVars <- c("x1.1", "x1.2", "x1.3", "x2.1", "x3.1_1_TEXT", "x3.9" )
for (col in numericVars) {
  sexual[[col]] <- as.numeric(as.character(sexual[[col]]))
}

# make var date
sexual$x1.4 <- as.Date(sexual$x1.4, format = "%d/%m/%Y")

# make var string
charVars <- c("x2.5_5_TEXT" , "x2.7_6_TEXT", "x2.10_8_TEXT", "x2.12_10_TEXT", "x2.14_5_TEXT", "x2.16_7_TEXT", "x2.21_9_TEXT", "x3.3_7_TEXT", "x3.13_8_TEXT", 
              "x3.14_7_TEXT", "x3.17_7_TEXT", "x4.10_1_TEXT", "x7.9_6_TEXT") 

for (col in charVars) {
  sexual[[col]] <- as.character(sexual[[col]])
}


#for (col in factorVars) {
  #data[[col]] <- as.factor(data[[col]])
#}


allVars <- names(sexual)
excludeVars <- c(numericVars, charVars, "x1.4")
factorVars <- setdiff(allVars, excludeVars)


for (col in factorVars) {
  sexual[[col]] <- as.character(sexual[[col]])
}
```

```{r}
# Get overlapping variables
common_vars <- intersect(names(sexual), names(labelled_data))

print(common_vars)

# Identify non-numeric variables
non_numeric_vars <- common_vars[
  sapply(common_vars, function(var) {
    !is.numeric(sexual[[var]]) && !is.numeric(labelled_data[[var]])
  })
]

# Apply labels to non-numeric overlapping variables only
for (var in non_numeric_vars) {
  var_label(sexual[[var]]) <- var_label(labelled_data[[var]])
  val_labels(sexual[[var]]) <- val_labels(labelled_data[[var]])
}

unique(sexual[["x2.2"]])
unique(sexual[["x3.10"]])

```

```{r}
sexual$x3.8_factor <- to_factor(sexual$x3.8, levels = "label")
sexual$x3.10_factor <- to_factor(sexual$x3.10, levels = "label")
sexual$x3.11_factor <- to_factor(sexual$x3.11, levels = "label")
sexual$x3.12_factor <- to_factor(sexual$x3.12, levels = "label")
sexual$x3.13_factor <- to_factor(sexual$x3.13, levels = "label")
sexual$x3.14_factor <- to_factor(sexual$x3.14, levels = "label")
sexual$x3.18_factor <- to_factor(sexual$x3.18, levels = "label")
sexual$x3.19_factor <- to_factor(sexual$x3.19, levels = "label")
sexual$x3.20_factor <- to_factor(sexual$x3.20, levels = "label")

sexual$x2.2_factor <- to_factor(sexual$x2.2, levels = "label")
```


```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.8_factor],
    COUNT(*) AS count
  FROM sexual
  GROUP BY [x2.2_factor], [x3.8_factor]
  ORDER BY [x2.2_factor], [x3.8_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.8_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```


```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.10_factor],
    COUNT(*) AS count
  FROM sexual
  GROUP BY [x2.2_factor], [x3.10_factor]
  ORDER BY [x2.2_factor], [x3.10_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.10_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```



```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.11_factor],
    COUNT(*) AS count
  FROM sexual
  GROUP BY [x2.2_factor], [x3.11_factor]
  ORDER BY [x2.2_factor], [x3.11_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.11_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x3.11_factor],
    COUNT(*) AS count
  FROM sexual
  GROUP BY [x2.1], [x3.11_factor]
  ORDER BY [x2.1], [x3.11_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.11_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```


```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.12_factor],
    COUNT(*) AS count
  FROM sexual
  GROUP BY [x2.2_factor], [x3.12_factor]
  ORDER BY [x2.2_factor], [x3.12_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.12_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.13_factor],
    COUNT(*) AS count
  FROM sexual
  GROUP BY [x2.2_factor], [x3.13_factor]
  ORDER BY [x2.2_factor], [x3.13_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.13_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```


```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.14_factor],
    COUNT(*) AS count
  FROM sexual
  GROUP BY [x2.2_factor], [x3.14_factor]
  ORDER BY [x2.2_factor], [x3.14_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.14_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```


```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.18_factor],
    COUNT(*) AS count
  FROM sexual
  GROUP BY [x2.2_factor], [x3.18_factor]
  ORDER BY [x2.2_factor], [x3.18_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.18_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.19_factor],
    COUNT(*) AS count
  FROM sexual
  GROUP BY [x2.2_factor], [x3.19_factor]
  ORDER BY [x2.2_factor], [x3.19_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.19_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.20_factor],
    COUNT(*) AS count
  FROM sexual
  GROUP BY [x2.2_factor], [x3.20_factor]
  ORDER BY [x2.2_factor], [x3.20_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.20_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```
## Pregnancy
```{r}
pregnancy <- fread("~/Desktop/GRIT/Kibera/subsetCsv/pregnancy.csv", header = TRUE)
labelled_data <- readRDS("~/Desktop/GRIT/Kibera/codebook/codebook_labelled_data.rds")
```

```{r}
# make var numeric
numericVars <- c("x1.1", "x1.2", "x1.3", "x2.1", "x3.1_1_TEXT", "x3.9" )
for (col in numericVars) {
  pregnancy[[col]] <- as.numeric(as.character(pregnancy[[col]]))
}

# make var date
pregnancy$x1.4 <- as.Date(pregnancy$x1.4, format = "%d/%m/%Y")

# make var string
charVars <- c("x2.5_5_TEXT" , "x2.7_6_TEXT", "x2.10_8_TEXT", "x2.12_10_TEXT", "x2.14_5_TEXT", "x2.16_7_TEXT", "x2.21_9_TEXT", "x3.3_7_TEXT", "x3.13_8_TEXT", 
              "x3.14_7_TEXT", "x3.17_7_TEXT", "x4.10_1_TEXT", "x7.9_6_TEXT") 

for (col in charVars) {
  pregnancy[[col]] <- as.character(pregnancy[[col]])
}


#for (col in factorVars) {
  #data[[col]] <- as.factor(data[[col]])
#}


allVars <- names(pregnancy)
excludeVars <- c(numericVars, charVars, "x1.4")
factorVars <- setdiff(allVars, excludeVars)


for (col in factorVars) {
  pregnancy[[col]] <- as.character(pregnancy[[col]])
}
```

```{r}
# Get overlapping variables
common_vars <- intersect(names(pregnancy), names(labelled_data))

print(common_vars)

# Identify non-numeric variables
non_numeric_vars <- common_vars[
  sapply(common_vars, function(var) {
    !is.numeric(pregnancy[[var]]) && !is.numeric(labelled_data[[var]])
  })
]

# Apply labels to non-numeric overlapping variables only
for (var in non_numeric_vars) {
  var_label(pregnancy[[var]]) <- var_label(labelled_data[[var]])
  val_labels(pregnancy[[var]]) <- val_labels(labelled_data[[var]])
}

unique(pregnancy[["x2.2"]])
unique(pregnancy[["x4.10"]])

```

```{r}
pregnancy$x4.8_factor <- to_factor(pregnancy$x4.8, levels = "label")
pregnancy$x4.16_factor <- to_factor(pregnancy$x4.16, levels = "label")
pregnancy$x4.17_factor <- to_factor(pregnancy$x4.17, levels = "label")
pregnancy$x4.20_factor <- to_factor(pregnancy$x4.20, levels = "label")
pregnancy$x4.22_factor <- to_factor(pregnancy$x4.22, levels = "label")
pregnancy$x2.2_factor <- to_factor(pregnancy$x2.2, levels = "label")
pregnancy$x6.2_factor <- to_factor(pregnancy$x6.2, levels = "label")

pregnancy$x5.1_factor <- to_factor(pregnancy$x5.1, levels = "label")
pregnancy$x5.23_factor <- to_factor(pregnancy$x5.23, levels = "label")


```


```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x4.16_factor],
    COUNT(*) AS count
  FROM pregnancy
  WHERE [x4.8] = 1
  GROUP BY [x2.1], [x4.16_factor]
  ORDER BY [x2.1], [x4.16_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x4.16_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x4.17_factor],
    COUNT(*) AS count
  FROM pregnancy
  WHERE [x4.8] = 1
  GROUP BY [x2.1], [x4.17_factor]
  ORDER BY [x2.1], [x4.17_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x4.17_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x4.20_factor],
    COUNT(*) AS count
  FROM pregnancy
  WHERE [x4.8] = 1
  GROUP BY [x2.1], [x4.20_factor]
  ORDER BY [x2.1], [x4.20_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x4.20_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x4.22_factor],
    COUNT(*) AS count
  FROM pregnancy
  WHERE [x4.8] = 1
  GROUP BY [x2.1], [x4.22_factor]
  ORDER BY [x2.1], [x4.22_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x4.22_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

pregnancy$x5.1_factor <- to_factor(pregnancy$x5.1, levels = "label")
pregnancy$x5.23_factor <- to_factor(pregnancy$x5.23, levels = "label")

```{r}

sql_result <- sqldf("
  SELECT
    [x2.1],
    [x5.1_factor],
    COUNT(*) AS count
  FROM pregnancy
  WHERE [x4.8] = 1
  GROUP BY [x2.1], [x5.1_factor]
  ORDER BY [x2.1], [x5.1_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x5.1_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x5.23_factor],
    COUNT(*) AS count
  FROM pregnancy
  WHERE [x4.8] = 1
  GROUP BY [x2.1], [x5.23_factor]
  ORDER BY [x2.1], [x5.23_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x5.23_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```





## Menstrual hygeine
```{r}
menstrual <- fread("~/Desktop/GRIT/Kibera/subsetCsv/menstrual.csv", header = TRUE)
labelled_data <- readRDS("~/Desktop/GRIT/Kibera/codebook/codebook_labelled_data.rds")
```

```{r}
# make var numeric
numericVars <- c("x1.1", "x1.2", "x1.3", "x2.1", "x3.1_1_TEXT", "x3.9" )
for (col in numericVars) {
  menstrual[[col]] <- as.numeric(as.character(menstrual[[col]]))
}

# make var date
menstrual$x1.4 <- as.Date(menstrual$x1.4, format = "%d/%m/%Y")

# make var string
charVars <- c("x2.5_5_TEXT" , "x2.7_6_TEXT", "x2.10_8_TEXT", "x2.12_10_TEXT", "x2.14_5_TEXT", "x2.16_7_TEXT", "x2.21_9_TEXT", "x3.3_7_TEXT", "x3.13_8_TEXT", 
              "x3.14_7_TEXT", "x3.17_7_TEXT", "x4.10_1_TEXT", "x7.9_6_TEXT") 

for (col in charVars) {
  menstrual[[col]] <- as.character(menstrual[[col]])
}


#for (col in factorVars) {
  #data[[col]] <- as.factor(data[[col]])
#}


allVars <- names(menstrual)
excludeVars <- c(numericVars, charVars, "x1.4")
factorVars <- setdiff(allVars, excludeVars)


for (col in factorVars) {
  menstrual[[col]] <- as.character(menstrual[[col]])
}
```

```{r}
# Get overlapping variables
common_vars <- intersect(names(menstrual), names(labelled_data))

print(common_vars)

# Identify non-numeric variables
non_numeric_vars <- common_vars[
  sapply(common_vars, function(var) {
    !is.numeric(menstrual[[var]]) && !is.numeric(labelled_data[[var]])
  })
]

# Apply labels to non-numeric overlapping variables only
for (var in non_numeric_vars) {
  var_label(menstrual[[var]]) <- var_label(labelled_data[[var]])
  val_labels(menstrual[[var]]) <- val_labels(labelled_data[[var]])
}

unique(menstrual[["x2.2"]])
unique(menstrual[["x4.10"]])

```

```{r}
menstrual$x3.1_factor <- to_factor(menstrual$x3.1, levels = "label")
menstrual$x3.2_factor <- to_factor(menstrual$x3.2, levels = "label")
menstrual$x3.3_factor <- to_factor(menstrual$x3.3, levels = "label")
menstrual$x3.4_factor <- to_factor(menstrual$x3.4, levels = "label")
menstrual$x3.5_factor <- to_factor(menstrual$x3.5, levels = "label")
menstrual$x3.6_factor <- to_factor(menstrual$x3.6, levels = "label")
menstrual$x3.7_factor <- to_factor(menstrual$x3.7, levels = "label")
menstrual$x2.2_factor <- to_factor(menstrual$x2.2, levels = "label")
```


```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x3.1_factor],
    COUNT(*) AS count
  FROM menstrual
  GROUP BY [x2.1], [x3.1_factor]
  ORDER BY [x2.1], [x3.1_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.1_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```


```{r}

sql_result <- sqldf("
  SELECT
    [x2.1],
    [x3.2_factor],
    COUNT(*) AS count
  FROM menstrual
  GROUP BY [x2.1], [x3.2_factor]
  ORDER BY [x2.1], [x3.2_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.2_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```
```{r}

sql_result <- sqldf("
  SELECT
    [x2.1],
    [x3.3_factor],
    COUNT(*) AS count
  FROM menstrual
  GROUP BY [x2.1], [x3.3_factor]
  ORDER BY [x2.1], [x3.3_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.3_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```




```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x3.4_factor],
    COUNT(*) AS count
  FROM menstrual
  GROUP BY [x2.1], [x3.4_factor]
  ORDER BY [x2.1], [x3.4_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.4_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x3.5_factor],
    COUNT(*) AS count
  FROM menstrual
  GROUP BY [x2.1], [x3.5_factor]
  ORDER BY [x2.1], [x3.5_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.5_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x3.6_factor],
    COUNT(*) AS count
  FROM menstrual
  GROUP BY [x2.1], [x3.6_factor]
  ORDER BY [x2.1], [x3.6_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.6_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x3.7_factor],
    COUNT(*) AS count
  FROM menstrual
  GROUP BY [x2.1], [x3.7_factor]
  ORDER BY [x2.1], [x3.7_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.7_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

## EDUCATION 
```{r}
education <- fread("~/Desktop/GRIT/Kibera/subsetCsv/education.csv", header = TRUE)
labelled_data <- readRDS("~/Desktop/GRIT/Kibera/codebook/codebook_labelled_data.rds")
```

```{r}
# make var numeric
numericVars <- c("x1.1", "x1.2", "x1.3", "x2.1", "x3.1_1_TEXT", "x3.9" )
for (col in numericVars) {
  education[[col]] <- as.numeric(as.character(education[[col]]))
}

# make var date
education$x1.4 <- as.Date(education$x1.4, format = "%d/%m/%Y")

# make var string
charVars <- c("x2.5_5_TEXT" , "x2.7_6_TEXT", "x2.10_8_TEXT", "x2.12_10_TEXT", "x2.14_5_TEXT", "x2.16_7_TEXT", "x2.21_9_TEXT", "x3.3_7_TEXT", "x3.13_8_TEXT", 
              "x3.14_7_TEXT", "x3.17_7_TEXT", "x4.10_1_TEXT", "x7.9_6_TEXT") 

for (col in charVars) {
  education[[col]] <- as.character(education[[col]])
}


#for (col in factorVars) {
  #data[[col]] <- as.factor(data[[col]])
#}


allVars <- names(education)
excludeVars <- c(numericVars, charVars, "x1.4")
factorVars <- setdiff(allVars, excludeVars)


for (col in factorVars) {
  education[[col]] <- as.character(education[[col]])
}
```

```{r}
# Get overlapping variables
common_vars <- intersect(names(education), names(labelled_data))

print(common_vars)

# Identify non-numeric variables
non_numeric_vars <- common_vars[
  sapply(common_vars, function(var) {
    !is.numeric(education[[var]]) && !is.numeric(labelled_data[[var]])
  })
]

# Apply labels to non-numeric overlapping variables only
for (var in non_numeric_vars) {
  var_label(education[[var]]) <- var_label(labelled_data[[var]])
  val_labels(education[[var]]) <- val_labels(labelled_data[[var]])
}

unique(education[["x2.2"]])

```


```{r}

education$x2.2_factor <- to_factor(education$x2.2, levels = "label")
```











## SEX EDUCATION
```{r}
sexEd <- fread("~/Desktop/GRIT/Kibera/subsetCsv/sexeducation.csv", header = TRUE)
labelled_data <- readRDS("~/Desktop/GRIT/Kibera/codebook/codebook_labelled_data.rds")
```

```{r}
# make var numeric
numericVars <- c("x1.1", "x1.2", "x1.3", "x2.1", "x3.1_1_TEXT", "x3.9" )
for (col in numericVars) {
  sexEd[[col]] <- as.numeric(as.character(sexEd[[col]]))
}

# make var date
sexEd$x1.4 <- as.Date(sexEd$x1.4, format = "%d/%m/%Y")

# make var string
charVars <- c("x2.5_5_TEXT" , "x2.7_6_TEXT", "x2.10_8_TEXT", "x2.12_10_TEXT", "x2.14_5_TEXT", "x2.16_7_TEXT", "x2.21_9_TEXT", "x3.3_7_TEXT", "x3.13_8_TEXT", 
              "x3.14_7_TEXT", "x3.17_7_TEXT", "x4.10_1_TEXT", "x7.9_6_TEXT") 

for (col in charVars) {
  sexEd[[col]] <- as.character(sexEd[[col]])
}


#for (col in factorVars) {
  #data[[col]] <- as.factor(data[[col]])
#}


allVars <- names(sexEd)
excludeVars <- c(numericVars, charVars, "x1.4")
factorVars <- setdiff(allVars, excludeVars)


for (col in factorVars) {
  sexEd[[col]] <- as.character(sexEd[[col]])
}
```

```{r}
# Get overlapping variables
common_vars <- intersect(names(sexEd), names(labelled_data))

print(common_vars)

# Identify non-numeric variables
non_numeric_vars <- common_vars[
  sapply(common_vars, function(var) {
    !is.numeric(sexEd[[var]]) && !is.numeric(labelled_data[[var]])
  })
]

# Apply labels to non-numeric overlapping variables only
for (var in non_numeric_vars) {
  var_label(sexEd[[var]]) <- var_label(labelled_data[[var]])
  val_labels(sexEd[[var]]) <- val_labels(labelled_data[[var]])
}

unique(sexEd[["x2.2"]])
unique(sexEd[["x4.10"]])

```



```{r}
sexEd$x3.12_factor <- to_factor(sexEd$x3.12, levels = "label")
sexEd$x4.16_factor <- to_factor(sexEd$x4.16, levels = "label")
sexEd$x5.14_factor <- to_factor(sexEd$x5.14, levels = "label")
sexEd$x2.2_factor <- to_factor(sexEd$x2.2, levels = "label")
```


```{r}
sql_result <- sqldf("
  SELECT
    [x2.1],
    [x3.12_factor],
    COUNT(*) AS count
  FROM sexEd
  GROUP BY [x2.1], [x3.12_factor]
  ORDER BY [x2.1], [x3.12_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.12_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```
```{r}
sql_result <- sqldf("
  SELECT
    [x2.2_factor],
    [x3.12_factor],
    COUNT(*) AS count
  FROM sexEd
  GROUP BY [x2.2_factor], [x3.12_factor]
  ORDER BY [x2.2_factor], [x3.12_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.12_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```



```{r}
sql_result <- sqldf("
  SELECT
    s.[x2.1],
    s.[x4.16_factor],
    COUNT(*) AS count
  FROM sexEd AS s
  JOIN pregnancy AS p
  ON p.[x1.2] = s.[x1.2]
  WHERE p.[x4.8] = 1
  GROUP BY s.[x2.1], s.[x4.16_factor]
  ORDER BY s.[x2.1], s.[x4.16_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x4.16_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```


```{r}
sql_result <- sqldf("
  SELECT
    s.[x2.1],
    s.[x5.14_factor],
    COUNT(*) AS count
  FROM sexEd AS s
  JOIN pregnancy AS p
  ON p.[x1.2] = s.[x1.2]
  WHERE p.[x4.8] = 1
  GROUP BY s.[x2.1], s.[x5.14_factor]
  ORDER BY s.[x2.1], s.[x5.14_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x5.14_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

## SUBSET SEX ED AND PREGNANCY

```{r}

x3.12_factor

sql_result <- sqldf("
  SELECT
    p.[x4.8_factor],
    s.[x3.12_factor],
    COUNT(*) AS count
  FROM sexEd AS s
  JOIN pregnancy AS p
  ON p.[x1.2] = s.[x1.2]
  WHERE p.[x4.8] = 1
  GROUP BY p.[x4.8_factor], s.[x3.12_factor]
  ORDER BY p.[x4.8_factor], s.[x3.12_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.12_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)




```

```{r}
sql_result <- sqldf("
  SELECT
    p.[x4.22_factor],
    s.[x3.12_factor],
    COUNT(*) AS count
  FROM sexEd AS s
  JOIN pregnancy AS p
  ON p.[x1.2] = s.[x1.2]
  WHERE p.[x4.8] = 1
  GROUP BY p.[x4.22_factor], s.[x3.12_factor]
  ORDER BY p.[x4.22_factor], s.[x3.12_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.12_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

## SUBSET SEX ED AND SEXUAL ACTIVITY

```{r}
sql_result <- sqldf("
  SELECT
    s.[x3.8_factor],
    e.[x3.12_factor],
    COUNT(*) AS count
  FROM sexEd AS e
  JOIN sexual AS s
  ON e.[x1.2] = s.[x1.2]
  GROUP BY s.[x3.8_factor], e.[x3.12_factor]
  ORDER BY s.[x3.8_factor], e.[x3.12_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x3.12_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```














## Subset domestic violence and mental health together

When you did not want them to, has someone ever... x mental health
```{r}
sql_result <- sqldf("
  SELECT
    m.[PHQ9Level],
    p.[x6.2_factor],
    COUNT(*) AS count
  FROM pregnancy AS p
    JOIN mentalHealth AS m
    ON p.[x1.2] = m.[x1.2]
  GROUP BY m.[PHQ9Level], p.[x6.2_factor]
  ORDER BY m.[PHQ9Level], p.[x6.2_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x6.2_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```




## Subset pregnancy and mental health together

```{r}
sql_result <- sqldf("
  SELECT
    m.[PHQ9Level],
    d.[x4.8_factor],
    COUNT(*) AS count
  FROM pregnancy AS d
    JOIN mentalHealth AS m
    ON d.[x1.2] = m.[x1.2]
  GROUP BY m.[PHQ9Level], d.[x4.8_factor]
  ORDER BY m.[PHQ9Level], d.[x4.8_factor]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x4.8_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```


##by Location

```{r}
sql_result <- sqldf("
  SELECT
    m.[PHQ9Level],
    p.[x4.8_factor],
    d.[x1.1],
    COUNT(*) AS count
  FROM pregnancy AS p
    JOIN mentalHealth AS m
      ON p.[x1.2] = m.[x1.2]
    JOIN demo AS d
      ON d.[x1.2] = m.[x1.2]
  GROUP BY m.[PHQ9Level], p.[x4.8_factor], d.[x1.1]
  ORDER BY d.[x1.1]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x4.8_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

##by age


```{r}
sql_result <- sqldf("
  SELECT
    m.[PHQ9Level],
    p.[x4.8_factor],
    d.[x2.1],
    COUNT(*) AS count
  FROM pregnancy AS p
    JOIN mentalHealth AS m
      ON p.[x1.2] = m.[x1.2]
    JOIN demo AS d
      ON d.[x1.2] = m.[x1.2]
  GROUP BY m.[PHQ9Level], p.[x4.8_factor], d.[x2.1]
  ORDER BY d.[x2.1]
")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x4.8_factor,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)
```

```{r}


sql_result <- sqldf("
  SELECT
    d.[x1.1],
    COUNT(*) AS count
  FROM pregnancy as p
  JOIN demo AS d
      ON d.[x1.2] = p.[x1.2]
  WHERE p.[x4.8] = 1
  GROUP BY d.[x1.1]

")

# Step 2: Pivot to make a wide table (Age as rows, Gender as columns)
pivot_table <- sql_result %>%
  pivot_wider(
    names_from = x1.1,
    values_from = count,
    values_fill = list(count = 0)
  )

pivot_table_totals <- pivot_table %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE)

# Step 3: View the table
print(pivot_table_totals)


```
```{r}
library(sqldf)
library(dplyr)
library(tidyr)

# 1. SQL query
sql_result <- sqldf("
  SELECT
    d.[x1.1] AS group_var,
    p.[x4.8] AS outcome_var,
    COUNT(*) AS count
  FROM pregnancy AS p
  JOIN demo AS d
    ON d.[x1.2] = p.[x1.2]
  GROUP BY d.[x1.1], p.[x4.8]
")

# 2. Convert to character to avoid haven_labelled issues
sql_result_clean <- sql_result %>%
  mutate(
    group_var   = as.character(group_var),
    outcome_var = as.character(outcome_var)
  )

# 3. Pivot to wide format
pivot_table <- sql_result_clean %>%
  pivot_wider(
    names_from  = outcome_var,
    values_from = count,
    values_fill = list(count = 0)
  )

# 4. Add a total row and total column
pivot_table_totals <- pivot_table %>%
  mutate(RowTotal = rowSums(across(where(is.numeric)))) %>%  # add total column
  bind_rows(                                                # add total row
    summarise(., across(where(is.numeric), sum)) %>%
      mutate(group_var = "TOTAL", RowTotal = sum(RowTotal))
  )

# 5. Print final table
print(pivot_table_totals)


```

```{r}
library(sqldf)
library(dplyr)
library(tidyr)

# 1. Get counts for each combo of x2.1 and x4.22_factor
sql_result <- sqldf("
  SELECT
    [x2.1]          AS group_var,
    [x4.22_factor]  AS outcome_var,
    COUNT(*)        AS count
  FROM pregnancy
  GROUP BY [x2.1], [x4.22_factor]
  ORDER BY [x2.1], [x4.22_factor]
")

# 2. Force to plain character (fixes haven_labelled issues)
sql_result_clean <- sql_result %>%
  mutate(
    group_var   = as.character(group_var),
    outcome_var = as.character(outcome_var)
  )

# 3. Pivot to wide:
# rows   = group_var (x2.1)
# cols   = outcome_var (x4.22_factor)
# values = count
pivot_table <- sql_result_clean %>%
  pivot_wider(
    names_from  = outcome_var,
    values_from = count,
    values_fill = list(count = 0)
  )

# 4. Add row totals and a final TOTAL row
pivot_table_totals <- pivot_table %>%
  # add total per row across all numeric columns
  mutate(RowTotal = rowSums(across(where(is.numeric)))) %>%
  # now bind a TOTAL row that sums each numeric column
  bind_rows(
    summarise(., across(where(is.numeric), sum)) %>%
      mutate(group_var = "TOTAL",
             RowTotal  = sum(RowTotal))
  )

# 5. View result
print(pivot_table_totals)

```




