---
title: "Kibera User Interface"
author: "Nicole Tang"
date: "2025"
output: html_document
runtime: shiny
---


```{r setup, include=FALSE}
library(shiny)
library(DBI)
library(RSQLite)
library(dplyr)
library(DT)
library(stringr)

# Path to your SQLite DB
db_path <- "~/Desktop/GRIT/Kibera/csv4db/kibera_survey.sqlite"

# Connect
con <- dbConnect(SQLite(), db_path)

# List columns from master table
master_columns <- dbListFields(con, "master")


```

```{r, echo=FALSE}

fluidPage(

    # Codebook link
    tags$div(
        style = "margin-bottom: 15px;",
        tags$a(
            href = "https://docs.google.com/spreadsheets/d/1J9xJLYzacIQPhaeuDCdkEWLOpli0vMrk72n_T1QTtGE/edit?gid=1118359261#gid=1118359261",
            class = "btn btn-primary",
            target = "_blank",
            "Kibera Codebook"
        )
    ),

    titlePanel("Kibera Survey Query Tool"),

    sidebarLayout(

        sidebarPanel(
            h4("Choose Columns for Analysis"),

            #selectInput("value_col", "Column to Summarize:", master_columns),
            selectInput("group_col", "Group By:", master_columns),
            actionButton("run_query", "Run Query"),   # ✅ FIXED — added comma

            br(), br(),
            downloadButton("download_grouped", "Download Grouped Table as CSV"),

            hr(),

            checkboxInput(
                "enable_pivot",
                "Enable Pivot Table for Custom Query",
                value = FALSE
            ),

            uiOutput("pivot_selectors_ui")
        ),

        mainPanel(

            h3("Query Results (Long Table)"),
            DTOutput("grouped_table"),

            hr(),

            h3("Custom SQL Query"),
            p("Use this section to run more complex queries directly on the Kibera database."),

            textAreaInput(
                "custom_sql",
                "Enter SQL Query:",
                height = "150px",
                width = "100%",
                value = "SELECT * FROM master LIMIT 10;"
            ),

            actionButton("run_custom", "Run Custom Query", class = "btn-success"),

            br(), br(),

            downloadButton("download_custom", "Download Custom Query as CSV"),

            br(), br(),

            DTOutput("custom_results"),

            hr(),

            h3("Pivot Table From Custom Query"),
            DTOutput("pivot_custom_table"),
            br(),
            downloadButton("download_pivot", "Download Pivot Table as CSV")
        )
    )
)


```



```



```{r, echo=FALSE}



observeEvent(input$run_query, {

    req(input$group_col)

    group_col <- input$group_col

    sql <- paste0(
        "SELECT ",
        group_col, " AS group_value, ",
        "COUNT(*) AS count ",
        "FROM master ",
        "GROUP BY ", group_col, ";"
    )

    grouped <- dbGetQuery(con, sql)

    output$grouped_table <- renderDT({
        datatable(grouped, rownames = FALSE)
    })

    output$download_grouped <- downloadHandler(
        filename = function() paste0("grouped_results_", Sys.Date(), ".csv"),
        content = function(file)
            write.csv(grouped, file, row.names = FALSE)
    )
})



custom_results_reactive <- reactiveVal(NULL)

observeEvent(input$run_custom, {

    tryCatch({

        res <- dbGetQuery(con, input$custom_sql)
        custom_results_reactive(res)

        output$custom_results <- renderDT({
            datatable(res, rownames = FALSE)
        })

    }, error = function(e) {

        output$custom_results <- renderDT({
            datatable(data.frame(Error = e$message), rownames = FALSE)
        })

    })
})


# ✅ Download custom SQL results
output$download_custom <- downloadHandler(
    filename = function() paste0("custom_query_results_", Sys.Date(), ".csv"),
    content = function(file) {
        df <- custom_results_reactive()
        if (!is.null(df)) write.csv(df, file, row.names = FALSE)
    }
)




output$pivot_selectors_ui <- renderUI({

    req(input$enable_pivot)
    req(custom_results_reactive())

    cols <- names(custom_results_reactive())

    tagList(
        selectInput("pivot_row", "Pivot Row:", choices = cols),
        selectInput("pivot_col", "Pivot Column:", choices = cols),
        actionButton("run_pivot", "Generate Pivot Table", class = "btn-info"),
        br(), br()
    )
})


pivot_data_reactive <- reactiveVal(NULL)


observeEvent(input$run_pivot, {

    req(custom_results_reactive())

    df <- custom_results_reactive()
    df <- mutate_all(df, as.character)

    # ✅ If SQL query included a 'count' column, expand back to row-level
    if ("count" %in% names(df)) {
        df <- tidyr::uncount(df, weights = as.integer(df$count))
    }

    # ✅ Always compute counts fresh for pivot
    pivot <- df |>
        group_by(.data[[input$pivot_row]], .data[[input$pivot_col]]) |>
        summarise(n = n(), .groups = "drop") |>
        tidyr::pivot_wider(
            names_from = .data[[input$pivot_col]],
            values_from = n,
            values_fill = list(n = 0)
        )

    pivot$Total <- rowSums(pivot[, -1], na.rm = TRUE)
    total_row <- c("Total", colSums(pivot[, -1], na.rm = TRUE))
    pivot <- rbind(pivot, total_row)

    colnames(pivot)[1] <- input$pivot_row

    pivot_data_reactive(pivot)

    output$pivot_custom_table <- renderDT({
        datatable(pivot, rownames = FALSE)
    })
})



# ✅ Download pivot table
output$download_pivot <- downloadHandler(
    filename = function() paste0("pivot_table_", Sys.Date(), ".csv"),
    content = function(file)
        write.csv(pivot_data_reactive(), file, row.names = FALSE)
)


```


